Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-09-15 sections/pitfalls.tex
weniger breite Zeilen, sonst keine Änderung
stichpunkte ausformuliert

@@

@@

	 		mechanical shutters? limited switching frequency
	 			switch beams by switching akkusto-optical modulators (AOM)

adjusting focal plane of the optical setup might lead to mismatch in superimposition of excitation and depletion beam

>>>>

Especially the second option tracing the cell surface would require constant
focal plane adjustment of the optical setup. This might eventually lead to a
mismatch in the excitation and depletion beam superimposition.

@@

The switching of the laser beams could either be done via mechanical
shutters. However, as mechanical shutters have a limited switching frequency,
it might be preferential to switch beams by switching akkusto-optical modulators.

@@
